### 2022-03-22 Journal1/Response1/Response.tex

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 3} \\
\hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``The authors propose a resource allocation scheme for network slicing in an Open RAN scenario. They consider three network slice types namely eMBB, URLLC and mMTC and provide a solution for end-to-end slicing considering resource allocation over the RAN domain following the proposed ORAN architecture, as well as VNF allocation. In general, the paper is well written, however some parts need to be rephrased and restructured.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of our manuscript and for
the thoughtful comments and constructive suggestions, which helped us to improve
the quality of this manuscript. We hope that the modifications that we have made to the manuscript, and the
responses that we have provided herein will alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The paper presents an interesting solution and an extremely well formulated mathematical problem; however, the main contribution of the paper is hard to grasp. For instance, the introduction of the paper is very generic. There are a lot of concepts and methods explained, nonetheless not related to the proposed solution. The main issue lies in the structure of the work. The main contribution only appears at the end of page 2, where after an extensive reading the interest of the reader starts to vanish. I would definitely suggest a restructuring here. For instance, directly hint the main objectives and motivation of the work to prepare the reader for what is following. Moreover, the Related work could be a section of its own. In that way, the organization of the paper is clearer and easier to read.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for the comment.  The introduction of the paper has been modified based on this comment. We have shortened the description of the state of the arts and the literature and briefly explained our goal before the main contribution section. We removed additional information and talked more about our work. We released non-related parts to clarify our goal. We hint at our motivation in the second paragraph of our first page and discuss our aim in the introduction.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Finally, a better distinction of the current proposal from the state-of-the-art is mandatory, otherwise it is hard to understand how the proposed algorithm differs from existing works in the literature which seem to provide solution to a similar problem.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The purpose of this paper is twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system.
In this paper, we would like to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.

In this paper, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
\begin{itemize}
\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC. Within the O-RAN architecture, the problem of radio resource allocation and VNF activation is explored.
Based on different types of services with different QoS and service priorities, we formulate a problem for the allocation of baseband resources to maximize the weighted throughput of O-RAN.
\item We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers. Therefore, we focus on obtaining the optimal number of VNFs in each layer of the O-RAN architecture. 
\item Different services need to consider varying QoS conditions, including delay, power, and throughput. According to the number of activated VNFs and the throughput of the users, we calculate the end-to-end processing delay of the system.
Assuming a limited fronthaul capacity, we calculate each O-RU's actual power and capacity. Depending on the service type, we model the interference of neighboring O-RUs and determine the actual throughput. Our model accounts for the short packet transmission of URLLC, and mMTC, which cannot be modeled by the Shannon capacity theorem.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``Furthermore, while the math introduced in the paper is solid, it is also hard to follow for a reader if illustrations are not presented. It would be easier if a Figure is introduced for instance to explain equations from 3a -3d, where a lot of variables are presented. Especially, for the concepts of inter and intra slice isolation, which are very crucial. Following, that logic more elaboration especially with respect to inter slice isolation and why it needs to be considered in the equation, is important, as one could say that a careful scheduling has to definitely avoid distribution of the same resources within a slice to different users i.e., (orthogonality constraint).''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is my pleasure to thank you for your comment, which helped me display and rectify the system model.
We added this part in the system model.

Assume there are $K$ physical resource blocks (PRBs) in the system. Suppose each slice $s$ consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.

A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$. Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.

Network Slicing techniques significantly reduce inter-service interference.
Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference. One of these methods is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC  [2], [6], [34]. In this paper, we assume that the PRB scheduling is performed. Also, in subsection II-F1, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
$I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.

@@

Also, we added a new subsection II-E-1 discyussing PRB scheduling for this question.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 4:} ``Additionally, since the authors claim their novelty on the introduction of ORAN architecture, it becomes of utmost importance to consider concepts such as the creation of a slice, management of a slice and well as deletion, which bridge the mathematical framework to the practical one. For instance, how is a network slice created in the proposed work? How are the requirements of a slice fed to the algorithm? How is the monitoring of a slice performed?''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I am grateful for this comment that makes the paper more practical.

In this subsection, we will look at the life cycle of network slicing on a practical level. 
The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning [38]. 
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice. 
\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.
\end{itemize}
In the preparation phase, the evaluation of requirements is considered. After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation. Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
